---
title: Software usage P1 - software characteristics
  html_notebook: default
Description: This is a notebook for genrating software characteristics graphs section. 
Inputs: processed - filtered_data_215rows.csv
  
Update: Computed all the characteristics after splitting the data based on the discipline
---


Plotting Software Usage
```{r}
#install.packages('plyr')
#install.packages('formattable')
library(plyr)
library(ggplot2)
library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#library(Rmisc)

#Read Data from file
#filteredx3 <- read.csv("filtered_data_215rows.csv")
filteredx3 <- read.csv("../../filtered_data_215rows_institute.csv")


#Count for frequency of categeorical variable in a data frame 
#, ylim=c(0,100),
#https://www.r-bloggers.com/how-to-get-the-frequency-table-of-a-categorical-variable-as-a-data-frame-in-r
#pdf("graphs/Rstudio_graphs/usage.pdf")
par(mfrow=c(2,2))
#Write software
use_SC_freq=count(filteredx3, 'write_SC')
use_SC_freq<-use_SC_freq[-c(4),]
use_SC_freq_sorted <- arrange(use_SC_freq, desc(use_SC_freq$freq))
tot = sum(use_SC_freq_sorted$freq)
xx<- barplot((use_SC_freq_sorted$freq/tot)*100, col=c("steelblue", "lightsteelblue1", "royalblue4"), cex.names=1.2,  cex.lab=1.2, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.2, ylim=c(0,101), main="Do you write source code?")
text(x = xx, y = ((use_SC_freq_sorted$freq/tot)*100),label=round((use_SC_freq_sorted$freq/tot)*100,2), pos = 3, cex = 1.2)



#Use software
#
use_SC_freq=count(filteredx3, 'use_SC')
use_SC_freq<-use_SC_freq[-c(4),]
use_SC_freq_sorted <- arrange(use_SC_freq, desc(use_SC_freq$freq))
tot = sum(use_SC_freq_sorted$freq)
xx<- barplot((use_SC_freq_sorted$freq/tot)*100, col=c("steelblue", "lightsteelblue1", "royalblue4"), ylim=c(0,101), cex.names=1.2,  cex.lab=1.2, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.2,main="Do you use source code written by others?")
text(x = xx, y = ((use_SC_freq_sorted$freq/tot)*100),label=round((use_SC_freq_sorted$freq/tot)*100,2), pos = 3, cex = 1.2)

#Write executables
#,
use_SC_freq=count(filteredx3, 'create_exe')
use_SC_freq<-use_SC_freq[-c(4),]
use_SC_freq_sorted <- arrange(use_SC_freq, desc(use_SC_freq$freq))
tot = sum(use_SC_freq_sorted$freq)
xx<- barplot((use_SC_freq_sorted$freq/tot)*100, col=c("steelblue", "lightsteelblue1", "royalblue4"), ylim=c(0,100), cex.names=1.3,  cex.lab=1.3,  las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.3, main="Do you create executables?")
text(x = xx, y = ((use_SC_freq_sorted$freq/tot)*100),label=round((use_SC_freq_sorted$freq/tot)*100,2), pos = 3, cex = 1.2)

#Use executables
#,
use_SC_freq=count(filteredx3, 'use_exe')
use_SC_freq<-use_SC_freq[-c(4),]
use_SC_freq_sorted <- arrange(use_SC_freq, desc(use_SC_freq$freq))
tot = sum(use_SC_freq_sorted$freq)
xx<- barplot((use_SC_freq_sorted$freq/tot)*100, col=c("steelblue", "lightsteelblue1", "royalblue4"), ylim=c(0,100), cex.names=1.2,  cex.lab=1.2, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.2, main="Do you use others' executables?")
text(x = xx, y = ((use_SC_freq_sorted$freq/tot)*100),label=round((use_SC_freq_sorted$freq/tot)*100,2), pos = 3, cex = 1.2)

#dev.off()


```


## Plotting Software Usage based on on discipline


usage_creat_exe_cs

```{r}
#pdf("graphs/Rstudio_graphs/usage_creat_exe_cs.pdf")

library(plyr)
library(dplyr) 
library(tidyr)

#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
library(Rmisc)


demo_data <- read.csv("../../filtered_data_215rows_institute.csv")


#Read and filter Data 
filtered_data_cs <- demo_data %>%
  filter(demo_data$QID7 == 'Computer Science')  %>%
  select(QID7,create_exe)

filtered_data_noncs <- demo_data %>%
  filter(demo_data$QID7 != 'Computer Science')  %>%
  select(QID7,create_exe)


training_freq1=na.omit(count(filtered_data_noncs, 'create_exe'))
training_freq1_sorted <- arrange(training_freq1, desc(training_freq1$freq))
tot1 = sum(training_freq1_sorted$freq)
#tot1
training_freq2=na.omit(count(filtered_data_cs, 'create_exe'))
training_freq2 <- rbind(training_freq2, c("I don't know", as.numeric(0)))
training_freq2$freq <- as.numeric(training_freq2$freq)
training_freq2$freq

training_freq2_sorted <- arrange(training_freq2, desc(training_freq2$freq))
#training_freq2_sorted
tot2 = sum(training_freq2_sorted$freq)
#tot2

xx <- (training_freq1_sorted$freq/tot1)*100
yy <- (training_freq2_sorted$freq/tot2)*100

#training_df = t(as.matrix(training_freq1_sorted$freq, training_freq2_sorted$freq))

training_df = data.frame((training_freq1_sorted$freq/tot1)*100, (training_freq2_sorted$freq/tot2)*100)
training_df
xx<- barplot(t(as.matrix(training_df)), col=c("steelblue", "pink2"), cex.names=1.2,  cex.lab=1.2, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.2, beside = T, ylim=c(0,100), ylab="%")
#text(x = xx, y = ((training_freq2_sorted$freq/tot)*100),label=percent(training_freq2_sorted$freq/tot), pos = 3, cex = 1.3)

xx
write.csv(training_df, file = "create_exe_data.csv")
text(x = xx[1,], y = ((training_freq1_sorted$freq/tot1)*100),label=round(((training_freq1_sorted$freq/tot1)*100),2), pos = 3, cex = 1.1)
text(x = xx[2,], y = ((training_freq2_sorted$freq/tot2)*100),label=round(((training_freq2_sorted$freq/tot2)*100),2), pos = 3, cex = 1.1)
legend("topright", c("Non-CS","CS"), cex=1,  col=c("steelblue", "pink2"),  pch=20)
chisq.test(training_df)
#dev.off()
#173
#38
```
write_SC

```{r}

#pdf("graphs/Rstudio_graphs/usage_write_sc_cs.pdf")

library(dplyr) 
library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#library(Rmisc)

#Read and filter Data 
filtered_data_cs <- demo_data %>%
  filter(demo_data$QID7 == 'Computer Science')  %>%
  select(QID7,write_SC)

filtered_data_noncs <- demo_data %>%
  filter(demo_data$QID7 != 'Computer Science')  %>%
  select(QID7,write_SC)

levels(filtered_data_cs$write_SC)
filtered_data_cs$write_SC


count(filtered_data_cs, 'write_SC')



training_freq1=count(filtered_data_noncs, 'write_SC')

#training_freq1<-training_freq1[-c(4),]
training_freq1_sorted <- arrange(training_freq1, desc(training_freq1$freq))
tot1 = sum(training_freq1_sorted$freq)

training_freq2=na.omit(count(filtered_data_cs, 'write_SC'))
training_freq2 <- rbind(training_freq2, c("I don't know", as.numeric(0)))
training_freq2$freq <- as.numeric(training_freq2$freq)
training_freq2$freq
#training_freq1<-training_freq1[-c(4),]
training_freq2_sorted <- arrange(training_freq2, desc(training_freq2$freq))

training_freq2_sorted
tot2 = sum(training_freq2_sorted$freq)
tot2

xx <- (training_freq1_sorted$freq/tot1)*100
yy <- (as.numeric(training_freq2_sorted$freq)/tot2)*100


#training_df = t(as.matrix(training_freq1_sorted$freq, training_freq2_sorted$freq))

training_df = data.frame((training_freq1_sorted$freq/tot1)*100, (as.numeric(training_freq2_sorted$freq/tot2)*100))
xx<- barplot(t(as.matrix(training_df)), col=c("steelblue", "pink2"), cex.names=1.2,  cex.lab=1.2, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.2, beside = T, ylim=c(0,105), ylab="%")
#text(x = xx, y = ((training_freq2_sorted$freq/tot)*100),label=percent(training_freq2_sorted$freq/tot), pos = 3, cex = 1.3)

chisq.test(training_df)

text(x = xx[1,], y = ((training_freq1_sorted$freq/tot1)*100),label=round(((training_freq1_sorted$freq/tot1)*100),2), pos = 3, cex = 1.1)
text(x = xx[2,], y = ((training_freq2_sorted$freq/tot2)*100),label=round(((training_freq2_sorted$freq/tot2)*100),2), pos = 3, cex = 1.1)
legend("topright", c("Non-CS","CS"), cex=1,  col=c("steelblue", "pink2"),  pch=20)
#dev.off()

```

Use sc discipline

```{r}


#pdf("graphs/Rstudio_graphs/usage_use_sc_cs.pdf")

library(dplyr) 
library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#library(Rmisc)

#Read and filter Data 
filtered_data_cs <- demo_data %>%
  filter(demo_data$QID7 == 'Computer Science')  %>%
  select(QID7,use_SC)

filtered_data_noncs <- demo_data %>%
  filter(demo_data$QID7 != 'Computer Science')  %>%
  select(QID7,use_SC)

training_freq1=count(filtered_data_noncs, 'use_SC')

#training_freq1<-training_freq1[-c(4),]
training_freq1_sorted <- arrange(training_freq1, desc(training_freq1$freq))
tot1 = sum(training_freq1_sorted$freq)
tot1
training_freq2=count(filtered_data_cs, 'use_SC')
#solve the problem of don't know choice by adding a row manually and convert the type of the whole column into numeric
training_freq2 <- rbind(training_freq2, c("I don't know", 0))
training_freq2$freq <- as.numeric(training_freq2$freq)

training_freq2_sorted <- arrange(training_freq2, desc(training_freq2$freq))
tot2 = sum(training_freq2_sorted$freq)
tot2

xx <- (training_freq1_sorted$freq/tot1)*100
yy <- (training_freq2_sorted$freq/tot2)*100

training_df = data.frame((training_freq1_sorted$freq/tot1)*100, (as.numeric(training_freq2_sorted$freq/tot2)*100))
xx<- barplot(t(as.matrix(training_df)), col=c("steelblue", "pink2"), cex.names=1.2,  cex.lab=1.2, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.2, beside = T, ylim=c(0,105), ylab="%")
text(x = xx[1,], y = ((training_freq1_sorted$freq/tot1)*100),label=round(((training_freq1_sorted$freq/tot1)*100),2), pos = 3, cex = 1.1)
text(x = xx[2,], y = ((training_freq2_sorted$freq/tot2)*100),label=round(((training_freq2_sorted$freq/tot2)*100),2), pos = 3, cex = 1.1)
legend("topright", c("Non-CS","CS"), cex=1,  col=c("steelblue", "pink2"),  pch=20)

training_df
chisq.test(training_df)

#dev.off()
#[1] 174
#[1] 39
```
use exe discipline

```{r}


#pdf("graphs/Rstudio_graphs/usage_use_exe_cs.pdf")

library(dplyr) 
library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#library(Rmisc)

#Read and filter Data 
filtered_data_cs <- demo_data %>%
  filter(demo_data$QID7 == 'Computer Science')  %>%
  select(QID7,use_exe)

filtered_data_noncs <- demo_data %>%
  filter(demo_data$QID7 != 'Computer Science')  %>%
  select(QID7,use_exe)


#filtered_data_cs$QID26 <- factor(filtered_data_cs$QID26, levels=c("Yes",  "No", "I don't know"))
#notebook_freq_sorted =na.omit(count(filtered_data_cs, 'QID26'))
#notebook_freq_sorted <- notebook_freq_sorted[!(notebook_freq_sorted$QID26 =="Not applicable"),]
#tot = sum(notebook_freq_sorted$freq)

training_freq1=na.omit(count(filtered_data_noncs, 'use_exe'))
training_freq1
training_freq1_sorted <- arrange(training_freq1, desc(training_freq1$freq))
tot1 = sum(training_freq1_sorted$freq)
tot1
training_freq2=na.omit(count(filtered_data_cs, 'use_exe'))
training_freq2

#solve the problem of don't know choice by adding a row manually and convert the type of the whole column into numeric
training_freq2 <- rbind(training_freq2, c("I don't know", 0))
training_freq2$freq <- as.numeric(training_freq2$freq)
training_freq2_sorted <- arrange(training_freq2, desc(training_freq2$freq))

training_freq2_sorted
tot2 = sum(training_freq2_sorted$freq)
tot2

xx <- (training_freq1_sorted$freq/tot1)*100
yy <- (training_freq2_sorted$freq/tot2)*100


#training_df = t(as.matrix(training_freq1_sorted$freq, training_freq2_sorted$freq))

training_df = data.frame((training_freq1_sorted$freq/tot1)*100, (as.numeric(training_freq2_sorted$freq/tot2)*100))
xx<- barplot(t(as.matrix(training_df)), col=c("steelblue", "pink2"), cex.names=1.2,  cex.lab=1.2, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.2, beside = T, ylim=c(0,105), ylab="%")
#text(x = xx, y = ((training_freq2_sorted$freq/tot)*100),label=percent(training_freq2_sorted$freq/tot), pos = 3, cex = 1.3)

xx
text(x = xx[1,], y = ((training_freq1_sorted$freq/tot1)*100),label=round(((training_freq1_sorted$freq/tot1)*100),2), pos = 3, cex = 1.1)
text(x = xx[2,], y = ((training_freq2_sorted$freq/tot2)*100),label=round(((training_freq2_sorted$freq/tot2)*100),2), pos = 3, cex = 1.1)
legend("topright", c("Non-CS","CS"), cex=1,  col=c("steelblue", "pink2"),  pch=20)

chisq.test(training_df)

#dev.off()
#] 174
#[1] 38
```

Plot Source code versus commerial software usage

```{r}
#Plot Source code versus commerial software usage
library(plyr)
library(ggplot2)
library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#pdf("graphs/Rstudio_graphs/sw_type.pdf")
filteredx3 <- read.csv("filtered_data_215rows.csv")

repur_freq_sorted=na.omit(count(filteredx3, 'QID20'))
repur_freq_sorted <- repur_freq_sorted[!(repur_freq_sorted$QID20 =="Not applicable"),]
tot = sum(repur_freq_sorted$freq)

filteredx3$use_comm_sw <- factor(filteredx3$use_comm_sw, levels=c("Yes",  "No", "I don't know"))
use_comm_sw_freq_sorted=na.omit(count(filteredx3, 'use_comm_sw'))
tot_comm = sum(use_comm_sw_freq_sorted$freq)

#repur_freq_sorted <- repur_freq_sorted[!(repur_freq_sorted$QID20 =="Not applicable"),]
#use_comm_sw_freq<-use_comm_sw_freq[-c(4),]
#Sorting values in a column asce or Desc: use_comm_sw_freq_sorted <- arrange(use_comm_sw_freq, desc(use_comm_sw_freq$freq))

filteredx3$use_opensource <- factor(filteredx3$use_opensource, levels=c("Yes",  "No", "I don't know"))
use_sourcecode_freq_sorted=na.omit(count(filteredx3, 'use_opensource'))
tot_source = sum(use_sourcecode_freq_sorted$freq)
xx = cbind((use_sourcecode_freq_sorted$freq/214)*100, use_comm_sw_freq_sorted$freq/214*100)
#par(mar=c(5.1,4.1,6,2.1))
bb <- barplot(t(as.matrix(xx)), beside = T, col=c("darkturquoise", "lightcoral"), cex.names=1.2,  cex.lab=1.2, axis.lty = 1,  las= 1 ,  border = NA, names.arg=c("Yes", "No","I don't know"), ylim=c(0,105), ylab = c("%"), panel.first = grid(), cex=1.2)
text(x = bb, y = t(as.matrix(xx)),label =round(t(as.matrix(xx)),2), pos = 3, cex = 1.1, col = c("black", "black"))
legend("topright",leg = c("Open source","Commercial software"), col = c("darkturquoise", "lightcoral"), fill =c("darkturquoise", "lightcoral"),cex=1, border = NA)
#dev.off()
#lightseagreen
```
Code purpose

"QID19 - 8.	How do you use code or software? [Please check all that apply.]"
This question read data from different file than the other questions. 
```{r}
#Plot Code purpose
library(plyr)
library(ggplot2)
library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#pdf("graphs/Rstudio_graphs/code_purpose.pdf")
#filteredx3 <- read.csv("filtered_data_215rows.csv")
  par(mar=c(3, 12, 3, 3))

pur <- read.csv("data_for_r/code_purpose.txt", sep = "\t")
#sort values in the graph
pur_sorted<- arrange(pur, desc(pur$percentage))
bp <- barplot(pur_sorted$percentage,  names.arg=pur_sorted$purpose,  horiz=TRUE, col="steelblue", border= "white",  las=1, cex.names=1.2,  cex.lab=1.2,  xlab = c("%"), panel.first = grid() , cex=1.2, xlim = c(0,110))
text(y = bp-0.3, x = 6 ,label = pur_sorted$percentage, pos = 3, cex = 1)

#dev.off()
```

Code Repurpose
"QID20 - 9.	Have you ever repurposed your code or software (i.e. using it for a project other than the one for which it was originally created)?"
```{r}
library(plyr)
library(ggplot2)
library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#library(Rmisc)

#Read Data from file
filteredx3 <- read.csv("filtered_data_215rows.csv")

#pdf("graphs/Rstudio_graphs/repurpose.pdf")
#Steps: modify the order of the levels to Yes, No, I don't know., Ommit the rows with NA, then Remove the row of Not applicable. 
filteredx3$QID20 <- factor(filteredx3$QID20, levels=c("Yes",  "No", "I don't know"))
repur_freq_sorted=na.omit(count(filteredx3, 'QID20'))
repur_freq_sorted <- repur_freq_sorted[!(repur_freq_sorted$QID20 =="Not applicable"),]
tot = sum(repur_freq_sorted$freq)
tot
xx<- barplot((repur_freq_sorted$freq/tot)*100, col=c("steelblue", "lightsteelblue1", "royalblue4"), ylim=c(0,100),  las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(), cex=1.2, cex.names=1.2,  cex.lab=1.2, ylab = c("%"))
text(x = xx, y = ((repur_freq_sorted$freq/tot)*100),label=round(repur_freq_sorted$freq/tot,2), pos = 3, cex = 1.1)

#dev.off()
```


"QID22 - 11.	Does everyone in your lab or research group write code using the same programming language(s)?"

```{r}
library(plyr)
library(ggplot2)
library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#library(Rmisc)

#Read Data from file
filteredx3 <- read.csv("filtered_data_215rows.csv")
#Does everyone in your lab or research group write code \n using the same programming language(s)?

#Count for frequency of categeorical variable in a data frame 
#https://www.r-bloggers.com/how-to-get-the-frequency-table-of-a-categorical-variable-as-a-data-frame-in-r
#pdf("graphs/Rstudio_graphs/collaboration_coding1.pdf")
#Change the levels order in a plot to a specific order.
filteredx3$QID22 <- factor(filteredx3$QID22, levels=c("Yes",  "No", "I don't know"))
lab_code_freq_sorted=na.omit(count(filteredx3, 'QID22'))
#lab_code_freq_sorted <- arrange(lab_code_freq, desc(lab_code_freq$freq))
lab_code_freq_sorted
lab_code_freq_sorted <- lab_code_freq_sorted[!(lab_code_freq_sorted$QID22 =="Not applicable"),]
#lab_code_freq_sorted<-lab_code_freq_sorted[-c(4),]
lab_code_freq_sorted
tot = sum(lab_code_freq_sorted$freq)
tot
xx<- barplot((lab_code_freq_sorted$freq/tot)*100, col=c("steelblue", "lightsteelblue1", "royalblue4"), ylim=c(0,70), cex.names=1.2, cex.lab=1.2, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(), cex=1.2, ylab = "%")
text(x = xx, y = ((lab_code_freq_sorted$freq/tot)*100),label=round((lab_code_freq_sorted$freq/tot)*100,2), pos = 3, cex = 1)

#dev.off()
```


"QID25 - 14.	Do you write code collaboratively (i.e. with another person or multiple people)?"

```{r}
library(plyr)
library(ggplot2)
library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#library(Rmisc)

#Read Data from file
filteredx3 <- read.csv("filtered_data_215rows.csv")

filteredx3$QID22 <- factor(filteredx3$QID25, levels=c("Yes",  "No", "I don't know"))

#Count for frequency of categeorical variable in a data frame 
#https://www.r-bloggers.com/how-to-get-the-frequency-table-of-a-categorical-variable-as-a-data-frame-in-r
#pdf("graphs/Rstudio_graphs/collaboration_coding2.pdf")
#na.omit is for excluding NAs
col_code_freq=na.omit(count(filteredx3, 'QID25'))
col_code_freq_sorted <- arrange(col_code_freq, desc(col_code_freq$freq))
col_code_freq_sorted
col_code_freq_sorted <- col_code_freq_sorted[!(col_code_freq_sorted$QID25 =="Not applicable"),]
#Remove row  by its index: col_code_freq_sorted<-col_code_freq_sorted[-c(4),]
col_code_freq_sorted
tot = sum(col_code_freq_sorted$freq)
tot
xx<- barplot((col_code_freq_sorted$freq/tot)*100, col=c("steelblue", "lightsteelblue1", "royalblue4"),ylim=c(0,70), cex.names=1.2, cex.lab=1.2,  las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(), cex=1.2, ylab = "%")
text(x = xx, y = ((col_code_freq_sorted$freq/tot)*100),label=round((col_code_freq_sorted$freq/sum(col_code_freq_sorted$freq))*100,2), pos = 3, cex = 1)

#dev.off()
```


