---
title: "Software usage P3 - Reproducibility"
output: html_notebook
Description: This is a notebook for genrating reproducibility graphs section. 
* Training based on Discipline and institutions - QID12
* Notebook usage- based on institution and discipline  - QID26
* Commenting based on the discipline - "QID23
* Do you generate documentation for your code?" - QID24


Input files: filtered_data_215rows.csv
---


Plotting Reproducibility Practices
```{r}

filteredx3$QID26 <- factor(filteredx3$QID26, levels=c("Yes",  "No", "I don't know"))
#Remove NA values
notebook_freq_sorted =na.omit(count(filteredx3, 'QID26'))
notebook_freq_sorted <- notebook_freq_sorted[!(notebook_freq_sorted$QID26 =="Not applicable"),]
tot = sum(notebook_freq_sorted$freq)

tot
xx<- barplot((notebook_freq_sorted$freq/tot)*100, col=c("steelblue", "lightsteelblue1", "royalblue4"), ylim=c(0,110), cex.names=1.2, cex.lab=1.3, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(), cex=1.2,ylab="%")


text(x = xx, y = ((notebook_freq_sorted$freq/tot)*100),label=round(notebook_freq_sorted$freq/sum(notebook_freq_sorted$freq),2), pos = 3, cex = 1.3)

```
### Reproducibility Practices 

"QID12 - 1.	Have you received training in coding conventions or best practices?"

```{r}
#filteredx3 <- read.csv("filtered_data_215rows.csv")
#install.packages('plyr')
#install.packages('formattable')
library(plyr)
library(ggplot2)
library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#library(Rmisc)

#Read Data from file
filteredx3 <- read.csv("filtered_data_215rows.csv")


#https://www.r-bloggers.com/how-to-get-the-frequency-table-of-a-categorical-variable-as-a-data-frame-in-r
#pdf("graphs/Rstudio_graphs/repro_training.pdf")
#Reproducibility Training
#Count the levels of the trainig column
training_freq=count(filteredx3, 'trainig')
training_freq<-training_freq[-c(4),]
training_freq_sorted <- arrange(training_freq, desc(training_freq$freq))
tot = sum(training_freq_sorted$freq)
tot
xx<- barplot((training_freq_sorted$freq/tot)*100, col=c("steelblue", "lightsteelblue1", "royalblue4"), ylim=c(0,100), cex.names=1.2,  cex.lab=1.2, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.2, ylab="%")
text(x = xx, y = ((training_freq_sorted$freq/tot)*100),label=round(((training_freq_sorted$freq/tot)*100),2), pos = 3, cex = 1.2)
#Have you received training in coding conventions or best practices?
#dev.off()

#**********************#
```


"QID23 - 12.	Do you include comments in your code?"

```{r}
library(plyr)
library(ggplot2)
library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#library(Rmisc)

#Read Data from file
filteredx3 <- read.csv("filtered_data_215rows.csv")

pdf("graphs/Rstudio_graphs/repro_comments.pdf")
filteredx3 <- read.csv("filtered_data_215rows.csv")
filteredx3$QID23 <- factor(filteredx3$QID23, levels=c("Yes",  "No", "I don't know"))
comments_freq_sorted =na.omit(count(filteredx3, 'QID23'))
comments_freq_sorted <- comments_freq_sorted[!(comments_freq_sorted$QID23 =="Not applicable"),]
tot = sum(comments_freq_sorted$freq)

tot
#Steps: modify the order of the levels to Yes, No, I don't know., Ommit the rows with NA, then Remove the row of Not applicable. 
xx<- barplot((comments_freq_sorted$freq/tot)*100, col=c("steelblue", "lightsteelblue1", "royalblue4"), ylim=c(0,110), cex.names=1.2, cex.lab=1.1, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(), cex=1.2, ylab="%")
text(x = xx, y = ((comments_freq_sorted$freq/tot)*100),label=round(((comments_freq_sorted$freq/tot)*100),2), pos = 3, cex = 1.1)
dev.off()

#**********************#
```


"QID24 - 13.	Do you generate documentation for your code?"

```{r}
library(plyr)
library(ggplot2)
library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#library(Rmisc)

#Read Data from file
filteredx3 <- read.csv("filtered_data_215rows.csv")

pdf("graphs/Rstudio_graphs/repro_documenting.pdf")

filteredx3$QID24 <- factor(filteredx3$QID24, levels=c("Yes",  "No", "I don't know"))
#Remove NA values
documenting_freq_sorted =na.omit(count(filteredx3, 'QID24'))
documenting_freq_sorted <- documenting_freq_sorted[!(documenting_freq_sorted$QID24 =="Not applicable"),]
tot = sum(documenting_freq_sorted$freq)

tot
xx<- barplot((documenting_freq_sorted$freq/tot)*100, col=c("steelblue", "lightsteelblue1", "royalblue4"), ylim=c(0,110), cex.names=1.2, cex.lab=1.2, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(), cex=1.2, ylab="%")


text(x = xx, y = ((documenting_freq_sorted$freq/tot)*100),label=round(((documenting_freq_sorted$freq/tot)*100),2), pos = 3, cex = 1.1)
dev.off()

#**********************#

```




```{r}
#filteredx3 <- read.csv("filtered_data_215rows.csv")
#install.packages('plyr')
#install.packages('formattable')

```


Training based on institution
```{r}
#https://www.r-bloggers.com/how-to-get-the-frequency-table-of-a-categorical-variable-as-a-data-frame-in-r
#pdf("graphs/Rstudio_graphs/repro_training_ucb.pdf")
#Reproducibility Training
#Count the levels of the trainig column 

library(dplyr) 

library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#library(Rmisc)

#Read Data from file

filtered_data_ucb <- demo_data %>%
  filter(demo_data$QID8 == 'UC Berkeley')  %>%
  select(QID8,trainig)

nrow(filtered_data_ucb)


filtered_data_nonucb <- demo_data %>%
  filter(demo_data$QID8 != 'UC Berkeley')  %>%
  select(QID8,trainig)

training_freq1=count(filtered_data_nonucb, 'trainig')
training_freq1_sorted <- arrange(training_freq1, desc(training_freq1$freq))
tot1 = sum(training_freq1_sorted$freq)
tot1
training_freq2=count(filtered_data_ucb, 'trainig')

training_freq2_sorted <- arrange(training_freq2, desc(training_freq2$freq))
tot2 = sum(training_freq2_sorted$freq)
tot2
training_freq2_sorted

xx <- (training_freq1_sorted$freq/tot1)*100
xx
yy <- (training_freq2_sorted$freq/tot2)*100
yy

#training_df = t(as.matrix(training_freq1_sorted$freq, training_freq2_sorted$freq))

training_df = data.frame((training_freq1_sorted$freq/tot1)*100, (training_freq2_sorted$freq/tot2)*100)
training_df
xx<- barplot(t(as.matrix(training_df)), col=c("steelblue", "pink2"), cex.names=1.2,  cex.lab=1.2, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No"), panel.first = grid(),cex=1.2, beside = T, ylim=c(0,70))
text(x = xx[1,], y = ((training_freq1_sorted$freq/tot1)*100),label=round(((training_freq1_sorted$freq/tot1)*100),2), pos = 3, cex = 1.1)
text(x = xx[2,], y = ((training_freq2_sorted$freq/tot2)*100),label=round(((training_freq2_sorted$freq/tot2)*100),2), pos = 3, cex = 1.1)
chisq.test(training_df)
legend("topright", c("Non-UCB","UCB"), cex=1,  col=c("steelblue", "pink2"),  pch=20)
chisq.test(training_df)
#dev.off()

```

training based on the discipline. note that training column is called trainig in the data. 

Check the training of reseachers based on their discpilines

```{r}
#pdf("graphs/Rstudio_graphs/repro_training_cs.pdf")


library(dplyr) 
library(tidyr) #this library for formatting the 0.97 to 97% throught percent() function
library(formattable)

#Read Data from file
#Split the data based on the discipline
filtered_data_cs <- demo_data %>%
  filter(demo_data$QID7 == 'Computer Science')  %>%
  select(QID7,trainig)

filtered_data_noncs <- demo_data %>%
  filter(demo_data$QID7 != 'Computer Science')  %>%
  select(QID7,trainig)



training_freq1=count(filtered_data_noncs, 'trainig')
training_freq1_sorted <- arrange(training_freq1, desc(training_freq1$freq))
tot1 = sum(training_freq1_sorted$freq)

training_freq2=count(filtered_data_cs, 'trainig')
#training_freq1<-training_freq1[-c(4),]
training_freq2_sorted <- arrange(training_freq2, desc(training_freq2$freq))
tot2 = sum(training_freq2_sorted$freq)

xx <- (training_freq1_sorted$freq/tot1)*100
xx
yy <- (training_freq2_sorted$freq/tot2)*100
yy

#training_df = t(as.matrix(training_freq1_sorted$freq, training_freq2_sorted$freq))

training_df = data.frame((training_freq1_sorted$freq/tot1)*100, (training_freq2_sorted$freq/tot2)*100)
training_df
xx<- barplot(t(as.matrix(training_df)), col=c("steelblue", "pink2"), cex.names=1.2,  cex.lab=1.2, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No"), panel.first = grid(),cex=1.2, beside = T, ylab="%", ylim = c(0,70))
text(x = xx[1,], y = ((training_freq1_sorted$freq/tot1)*100),label=round(((training_freq1_sorted$freq/tot1)*100),2), pos = 3, cex = 1)
text(x = xx[2,], y = ((training_freq2_sorted$freq/tot2)*100),label=round(((training_freq2_sorted$freq/tot2)*100),2), pos = 3, cex = 1)

legend("topright", c("Non-CS","CS"), cex=1.0,  col=c("steelblue", "pink2"),  pch=20)
chisq.test(training_df)
#dev.off()

```






Using electronic notebooks

"QID26 - 15.	Do you write code using a notebook? application (e.g. IPython, Jupyter, Zeppelin, Beaker)?"

```{r}
library(plyr)
library(ggplot2)
library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#library(Rmisc)

#Read Data from file
filteredx3 <- read.csv("filtered_data_215rows.csv")

pdf("graphs/Rstudio_graphs/repro_notebook.pdf")


filteredx3$QID26 <- factor(filteredx3$QID26, levels=c("Yes",  "No", "I don't know"))
#Remove NA values
notebook_freq_sorted =na.omit(count(filteredx3, 'QID26'))
notebook_freq_sorted <- notebook_freq_sorted[!(notebook_freq_sorted$QID26 =="Not applicable"),]
tot = sum(notebook_freq_sorted$freq)

tot
xx<- barplot((notebook_freq_sorted$freq/tot)*100, col=c("steelblue", "lightsteelblue1", "royalblue4"), ylim=c(0,110), cex.names=1.2, cex.lab=1.2, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(), cex=1.2, ylab="%")


text(x = xx, y = ((notebook_freq_sorted$freq/tot)*100),label=round(((notebook_freq_sorted$freq/tot)*100),2), pos = 3, cex = 1.1)
dev.off()



```




"QID26 - Do you write code using a notebook? application (e.g. IPython, Jupyter, Zeppelin, Beaker)?"
Based on Discipline
```{r}

#********************************#
#pdf("graphs/Rstudio_graphs/repro_notebook_cs.pdf")

#import libraries
library(dplyr) 
library(tidyr)
library(formattable)#this library for formatting the 0.97 to 97% throught percent() function
#Read Data 

#filter data based on institution
filtered_data_cs <- demo_data %>%
  filter(demo_data$QID7 == 'Computer Science')   %>%
  select(QID7,QID26)

head(filtered_data_cs)

filtered_data_noncs <- demo_data %>%
  filter(demo_data$QID7 != 'Computer Science')  %>%
  select(QID7,QID26)

  

#Sorting the value of each of the filtered data, relabel the factors to "Yes",  "No", "I don't know", omit the NA values, getting the sum of the count of each factor after excluding the NA.
filtered_data_noncs$QID26 <- factor(filtered_data_noncs$QID26, levels=c("Yes",  "No", "I don't know"))
notebook_freq_sorted1 =na.omit(count(filtered_data_noncs, 'QID26'))
notebook_freq_sorted1 <- notebook_freq_sorted1[!(notebook_freq_sorted1$QID26 =="Not applicable"),]
tot1 = sum(notebook_freq_sorted1$freq)


filtered_data_cs$QID26 <- factor(filtered_data_cs$QID26, levels=c("Yes",  "No", "I don't know"))
notebook_freq_sorted =na.omit(count(filtered_data_cs, 'QID26'))
#solve the problem of don't know choice by adding a row manually and convert the type of the whole column into numeric
notebook_freq_sorted <- rbind(notebook_freq_sorted, c("I don't know", 0))
notebook_freq_sorted$freq <- as.numeric(notebook_freq_sorted$freq)

notebook_freq_sorted <- notebook_freq_sorted[!(notebook_freq_sorted$QID26 =="Not applicable"),]
tot = sum(notebook_freq_sorted$freq)

tot


#Generate a data frame from the two filtered data 

training_df = data.frame((notebook_freq_sorted1$freq/tot1)*100, (notebook_freq_sorted$freq/tot)*100)
training_df
#Plot the data frame that has the values of filetred data 
xx<- barplot(t(as.matrix(training_df)), col=c("steelblue", "pink2"), cex.names=1.1,  cex.lab=1.1, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.1, beside = T,  ylim=c(0,65),ylab="%")

#instead of using percent function to print the percentage on the bars I used round and removed the % sign to save a space.
text(x = xx[1,], y = ((notebook_freq_sorted1$freq/tot1)*100),label=round(((notebook_freq_sorted1$freq/tot1)*100),2), pos = 3, cex = 1)
text(x = xx[2,], y = ((notebook_freq_sorted$freq/tot)*100),label=round(((notebook_freq_sorted$freq/tot)*100),2), pos = 3, cex = 1)
chisq.test(training_df)
legend("topright", c("Non-CS","CS"), cex=1,  col=c("steelblue", "pink2"),  pch=20)
#dev.off()

```


"QID26 - 15.	Do you write code using a notebook? application (e.g. IPython, Jupyter, Zeppelin, Beaker)?"
based on institution
```{r}
#pdf("graphs/Rstudio_graphs/repro_notebook_ucb.pdf")

#import libraries
library(dplyr) 
library(tidyr)
library(formattable)#this library for formatting the 0.97 to 97% throught percent() function
#Read Data 

#filter data based on institution
filtered_data_ucb <- demo_data %>%
  filter(demo_data$QID8 == 'UC Berkeley')  %>%
  select(QID8,QID26)

filtered_data_nonucb <- demo_data %>%
  filter(demo_data$QID8 != 'UC Berkeley')  %>%
  select(QID8,QID26)



#Sorting the value of each of the filtered data, relabel the factors to "Yes",  "No", "I don't know", omit the NA values, getting the sum of the count of each factor after excluding the NA.
filtered_data_nonucb$QID26 <- factor(filtered_data_nonucb$QID26, levels=c("Yes",  "No", "I don't know"))
notebook_freq_sorted1 =na.omit(count(filtered_data_nonucb, 'QID26'))
notebook_freq_sorted1 <- notebook_freq_sorted1[!(notebook_freq_sorted1$QID26 =="Not applicable"),]
tot1 = sum(notebook_freq_sorted1$freq)


filtered_data_ucb$QID26 <- factor(filtered_data_ucb$QID26, levels=c("Yes",  "No", "I don't know"))
notebook_freq_sorted =na.omit(count(filtered_data_ucb, 'QID26'))
notebook_freq_sorted <- notebook_freq_sorted[!(notebook_freq_sorted$QID26 =="Not applicable"),]
tot = sum(notebook_freq_sorted$freq)

tot


#Generate a data frame from the two filtered data 

training_df = data.frame((notebook_freq_sorted1$freq/tot1)*100, (notebook_freq_sorted$freq/tot)*100)
training_df
#Plot the data frame that has the values of filetred data 
xx<- barplot(t(as.matrix(training_df)), col=c("steelblue", "pink2"), cex.names=1.1,  cex.lab=1.1, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.1, beside = T,  ylim=c(0,65),ylab="%")

#instead of using percent function to print the percentage on the bars I used round and removed the % sign to save a space.
text(x = xx[1,], y = ((notebook_freq_sorted1$freq/tot1)*100),label=round(((notebook_freq_sorted1$freq/tot1)*100),2), pos = 3, cex = 1.1)
text(x = xx[2,], y = ((notebook_freq_sorted$freq/tot)*100),label=round(((notebook_freq_sorted$freq/tot)*100),2), pos = 3, cex = 1.1)
chisq.test(training_df)
legend("topright", c("Non-UCB","UCB"), cex=1,  col=c("steelblue", "pink2"),  pch=20)
#dev.off()

```



"QID23 - 12.	Do you include comments in your code?"
No difference between cd and other disciplines 


```{r}
#pdf("graphs/Rstudio_graphs/repro_comments_cs.pdf")



library(dplyr) 
library(tidyr)
library(formattable)#this library for formatting the 0.97 to 97% throught percent() function
#Read Data 

#filter data based on institution
filtered_data_cs <- demo_data %>%
  filter(demo_data$QID7 == 'Computer Science')  %>%
  select(QID7,QID23)

filtered_data_noncs <- demo_data %>%
  filter(demo_data$QID7 != 'Computer Science')  %>%
  select(QID7,QID23)



#Sorting the value of each of the filtered data, relabel the factors to "Yes",  "No", "I don't know", omit the NA values, getting the sum of the count of each factor after excluding the NA.
filtered_data_noncs$QID23 <- factor(filtered_data_noncs$QID23, levels=c("Yes",  "No", "I don't know"))
notebook_freq_sorted1 =na.omit(count(filtered_data_noncs, 'QID23'))
notebook_freq_sorted1 <- notebook_freq_sorted1[!(notebook_freq_sorted1$QID23 =="Not applicable"),]
tot1 = sum(notebook_freq_sorted1$freq)


filtered_data_cs$QID23 <- factor(filtered_data_cs$QID23, levels=c("Yes",  "No", "I don't know"))
notebook_freq_sorted =na.omit(count(filtered_data_cs, 'QID23'))
notebook_freq_sorted <- notebook_freq_sorted[!(notebook_freq_sorted$QID23 =="Not applicable"),]
notebook_freq_sorted <- rbind(notebook_freq_sorted, c("I don't know", 0))
notebook_freq_sorted$freq <- as.numeric(notebook_freq_sorted$freq)
tot = sum(notebook_freq_sorted$freq)

tot


#Generate a data frame from the two filtered data 

training_df = data.frame((notebook_freq_sorted1$freq/tot1)*100, (notebook_freq_sorted$freq/tot)*100)
training_df
#Plot the data frame that has the values of filetred data 
xx<- barplot(t(as.matrix(training_df)), col=c("steelblue", "pink2"), cex.names=1.1,  cex.lab=1.1, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.1, beside = T,  ylim=c(0,110),ylab="%")

#instead of using percent function to print the percentage on the bars I used round and removed the % sign to save a space.
text(x = xx[1,], y = ((notebook_freq_sorted1$freq/tot1)*100),label=round(((notebook_freq_sorted1$freq/tot1)*100),2), pos = 3, cex = 1.1)
text(x = xx[2,], y = ((notebook_freq_sorted$freq/tot)*100),label=round(((notebook_freq_sorted$freq/tot)*100),2), pos = 3, cex = 1.1)

legend("topright", c("Non-CS","CS"), cex=1,  col=c("steelblue", "pink2"),  pch=20)
chisq.test(training_df)

#dev.off()

#**********************#
```



"QID24 -	Do you generate documentation for your code?"

```{r}
#documenting_freq_sorted =na.omit(count(filteredx3, 'QID24'))

#pdf("graphs/Rstudio_graphs/repro_documenting_cs.pdf")

library(dplyr) 
library(tidyr)
library(formattable)#this library for formatting the 0.97 to 97% throught percent() function
#Read Data 

#filter data based on institution

#filter data based on institution
filtered_data_cs <- demo_data %>%
  filter(demo_data$QID7 == 'Computer Science')  %>%
  select(QID7,QID24)

filtered_data_noncs <- demo_data %>%
  filter(demo_data$QID7 != 'Computer Science')  %>%
  select(QID7,QID24)





#Sorting the value of each of the filtered data, relabel the factors to "Yes",  "No", "I don't know", omit the NA values, getting the sum of the count of each factor after excluding the NA.
filtered_data_noncs$QID24 <- factor(filtered_data_noncs$QID24, levels=c("Yes",  "No", "I don't know"))
notebook_freq_sorted1 =na.omit(count(filtered_data_noncs, 'QID24'))
notebook_freq_sorted1 <- notebook_freq_sorted1[!(notebook_freq_sorted1$QID24 =="Not applicable"),]
tot1 = sum(notebook_freq_sorted1$freq)


filtered_data_cs$QID24 <- factor(filtered_data_cs$QID24, levels=c("Yes",  "No", "I don't know"))
notebook_freq_sorted =na.omit(count(filtered_data_cs, 'QID24'))
notebook_freq_sorted <- notebook_freq_sorted[!(notebook_freq_sorted$QID24 =="Not applicable"),]
#notebook_freq_sorted <- rbind(notebook_freq_sorted, c("I don't know", 0))
#notebook_freq_sorted$freq <- as.numeric(notebook_freq_sorted$freq)
tot = sum(notebook_freq_sorted$freq)

tot


#Generate a data frame from the two filtered data 

training_df = data.frame((notebook_freq_sorted1$freq/tot1)*100, (notebook_freq_sorted$freq/tot)*100)
training_df
#Plot the data frame that has the values of filetred data 
xx<- barplot(t(as.matrix(training_df)), col=c("steelblue", "pink2"), cex.names=1.1,  cex.lab=1.1, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.1, beside = T,  ylim=c(0,80),ylab="%")

#instead of using percent function to print the percentage on the bars I used round and removed the % sign to save a space.
text(x = xx[1,], y = ((notebook_freq_sorted1$freq/tot1)*100),label=round(((notebook_freq_sorted1$freq/tot1)*100),2), pos = 3, cex = 1.1)
text(x = xx[2,], y = ((notebook_freq_sorted$freq/tot)*100),label=round(((notebook_freq_sorted$freq/tot)*100),2), pos = 3, cex = 1.1)

legend("topright", c("Non-CS","CS"), cex=1,  col=c("steelblue", "pink2"),  pch=20)
chisq.test(training_df)
#dev.off()

```



Plot the training in software question.

```{r}

#https://www.r-bloggers.com/how-to-get-the-frequency-table-of-a-categorical-variable-as-a-data-frame-in-r
#pdf("graphs/Rstudio_graphs/repro_training_UCB.pdf")
#Reproducibility Training
#Count the levels of the trainig column
training_freq=count(filteredx3, 'trainig')
training_freq<-training_freq[-c(4),]
training_freq_sorted <- arrange(training_freq, desc(training_freq$freq))
tot = sum(training_freq_sorted$freq)
tot
xx<- barplot((training_freq_sorted$freq/tot)
             *100, col=c("steelblue", "lightsteelblue1", "royalblue4"), ylim=c(0,100), cex.names=1.3,  cex.lab=1.3, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.3)
text(x = xx, y = ((training_freq_sorted$freq/tot)*100),label=percent(training_freq_sorted$freq/tot), pos = 3, cex = 1.3)
#Have you received training in coding conventions or best practices?
#dev.off()

#**********************#
```




Dependency information

"QID38 - 9.	When you share your code or software, do you provide information about dependencies?
```{r}
 
#library(Rmisc)
#pdf("graphs/Rstudio_graphs/dependency.pdf")
#N=174

#Read Data from file
#data_format <- read.csv("data_for_r/dependency.txt", sep = "\t")
#bp <- barplot(data_format$percentage*100,  names.arg=data_format$answer,  col=c("steelblue", "lightsteelblue1", "royalblue4"), border= "white",  las=1, cex.names=1.2,  cex.lab=1.2, panel.first = grid() , cex=1.2, ylim = c(0,85), axis.lty = 1)
#text(x = bp, y =(data_format$percentage*100) ,label = round(data_format$percentage*100,2), pos = 3, cex = 1.2)

#pdf("graphs/Rstudio_graphs/repro_dependency_cs.pdf")

library(dplyr) 
library(tidyr)
library(formattable)#this library for formatting the 0.97 to 97% throught percent() function
#Read Data 

#filter data based on institution

#filter data based on institution
filtered_data_cs <- demo_data %>%
  filter(demo_data$QID7 == 'Computer Science')  %>%
  select(QID7,QID38)

filtered_data_noncs <- demo_data %>%
  filter(demo_data$QID7 != 'Computer Science')  %>%
  select(QID7,QID38)





#Sorting the value of each of the filtered data, relabel the factors to "Yes",  "No", "I don't know", omit the NA values, getting the sum of the count of each factor after excluding the NA.
filtered_data_noncs$QID38 <- factor(filtered_data_noncs$QID38, levels=c("Yes",  "No", "I don't know"))
notebook_freq_sorted1 =na.omit(count(filtered_data_noncs, 'QID38'))
notebook_freq_sorted1 <- notebook_freq_sorted1[!(notebook_freq_sorted1$QID38 =="Not applicable"),]
tot1 = sum(notebook_freq_sorted1$freq)


filtered_data_cs$QID38 <- factor(filtered_data_cs$QID38, levels=c("Yes",  "No", "I don't know"))
notebook_freq_sorted =na.omit(count(filtered_data_cs, 'QID38'))
notebook_freq_sorted <- notebook_freq_sorted[!(notebook_freq_sorted$QID38 =="Not applicable"),]
notebook_freq_sorted <- rbind(notebook_freq_sorted, c("I don't know", 0))
notebook_freq_sorted$freq <- as.numeric(notebook_freq_sorted$freq)
tot = sum(notebook_freq_sorted$freq)

tot


#Generate a data frame from the two filtered data 

training_df = data.frame((notebook_freq_sorted1$freq/tot1)*100, (notebook_freq_sorted$freq/tot)*100)
training_df
#Plot the data frame that has the values of filetred data 
xx<- barplot(t(as.matrix(training_df)), col=c("steelblue", "pink2"), cex.names=1.1,  cex.lab=1.1, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.1, beside = T,  ylim=c(0,100),ylab="%")

#instead of using percent function to print the percentage on the bars I used round and removed the % sign to save a space.
text(x = xx[1,], y = ((notebook_freq_sorted1$freq/tot1)*100),label=round(((notebook_freq_sorted1$freq/tot1)*100),2), pos = 3, cex = 1.1)
text(x = xx[2,], y = ((notebook_freq_sorted$freq/tot)*100),label=round(((notebook_freq_sorted$freq/tot)*100),2), pos = 3, cex = 1.1)

legend("topright", c("Non-CS","CS"), cex=1,  col=c("steelblue", "pink2"),  pch=20)
chisq.test(training_df)



#dev.off()
```




"QID37 - 8 When you share your code or software, do you share it alongside related files (e.g. datasets)?


```{r}
 
#pdf("graphs/Rstudio_graphs/repro_related_files_cs.pdf")

library(dplyr) 
library(tidyr)
library(formattable)#this library for formatting the 0.97 to 97% throught percent() function
#Read Data 

#filter data based on institution

#filter data based on institution
filtered_data_cs <- demo_data %>%
  filter(demo_data$QID7 == 'Computer Science')  %>%
  select(QID7,QID37)

filtered_data_noncs <- demo_data %>%
  filter(demo_data$QID7 != 'Computer Science')  %>%
  select(QID7,QID37)


levels(filtered_data_cs$QID37)
levels(filtered_data_noncs$QID37)
#Yes (please describe)  
#- "I don't know"          "No"                    "Not applicable"       
#[4] "Yes (please describe)"

#Sorting the value of each of the filtered data, relabel the factors to "Yes",  "No", "I don't know", omit the NA values, getting the sum of the count of each factor after excluding the NA.
filtered_data_noncs$QID37 <- factor(filtered_data_noncs$QID37, levels=c("Yes (please describe)",  "No", "I don't know"))
notebook_freq_sorted1 =na.omit(count(filtered_data_noncs, 'QID37'))
notebook_freq_sorted1 <- notebook_freq_sorted1[!(notebook_freq_sorted1$QID37 =="Not applicable"),]
tot1 = sum(notebook_freq_sorted1$freq)


filtered_data_cs$QID37 <- factor(filtered_data_cs$QID37, levels=c("Yes (please describe)",  "No", "I don't know"))
notebook_freq_sorted =na.omit(count(filtered_data_cs, 'QID37'))
notebook_freq_sorted <- notebook_freq_sorted[!(notebook_freq_sorted$QID37 =="Not applicable"),]
notebook_freq_sorted <- rbind(notebook_freq_sorted, c("I don't know", 0))
notebook_freq_sorted$freq <- as.numeric(notebook_freq_sorted$freq)
tot = sum(notebook_freq_sorted$freq)

tot


#Generate a data frame from the two filtered data 

training_df = data.frame((notebook_freq_sorted1$freq/tot1)*100, (notebook_freq_sorted$freq/tot)*100)
training_df
chisq.test(training_df)

#Plot the data frame that has the values of filetred data 
xx<- barplot(t(as.matrix(training_df)), col=c("steelblue", "pink2"), cex.names=1.1,  cex.lab=1.1, las= 1, axis.lty = 1,  border = NA, names.arg=c("Yes", "No","I don't know"), panel.first = grid(),cex=1.1, beside = T,  ylim=c(0,100),ylab="%")

#instead of using percent function to print the percentage on the bars I used round and removed the % sign to save a space.
text(x = xx[1,], y = ((notebook_freq_sorted1$freq/tot1)*100),label=round(((notebook_freq_sorted1$freq/tot1)*100),2), pos = 3, cex = 1.1)
text(x = xx[2,], y = ((notebook_freq_sorted$freq/tot)*100),label=round(((notebook_freq_sorted$freq/tot)*100),2), pos = 3, cex = 1.1)
legend("topright", c("Non-CS","CS"), cex=1,  col=c("steelblue", "pink2"),  pch=20)


#dev.off()


```




```{r}
library(plyr)
library(ggplot2)
library(tidyr)
#this library for formatting the 0.97 to 97% throught percent() function
library(formattable)
#library(Rmisc)
pdf("graphs/Rstudio_graphs/code_related_files.pdf")
#N=174

#Read Data from file
data_format <- read.csv("data_for_r/code_related_files.txt", sep = "\t")
bp <- barplot(data_format$percentage*100,  names.arg=data_format$answer, col=c("steelblue", "lightsteelblue1", "royalblue4"), border= "white",  las=1, cex.names=1.2,  cex.lab=1.2, panel.first = grid() , cex=1.2, ylim = c(0,85), axis.lty = 1)
text(x = bp, y =(data_format$percentage*100) ,label = round(data_format$percentage*100,2), pos = 3, cex = 1.2)

dev.off()

```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
